\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-26 coq-example.tex
Reply the comments.

We construct four families, in one inheritance chain.\YZ{Why is it useful to define these concrete and abstract interpreters as an inheritance chain?}\EDJreply{I don't think these examples are here to show the example themselves are useful. They are here to show family inheritance is useful, and can extend stuff to all sorts of things. I also add some details below on how each family can be extended and what each family means.}\YZreply{Why is it desired to define the abstract interpreter as an extension of the concrete interpreter family? What is lost by putting the two interpreters in the same family?}

The first family "Lang" define the big step operator (using fuel) of a
while language, with expression. But it postulates the computational
information of "State" used by Lang. It takes about 200+ LOCs. We
can\YZ{In general, in a result section like this, you want to show what
you *have done* rather than what you *can do*.}
swap the implementation of "State" to have different memory/state
management by extending family "Lang".\YZ{What is 'different
memory/state management'?}

@@

The fourth family "LangRun" instantiate some of the postulates of the
LangMore and recover computational information of Lang. The concrete
interpreter is doing as expected; the abstract interpreter is expected
to act as a type-analyzer. It takes about 200+ LOCs. This is one example
of instantiate the detail computation. In this example, we use a simple
Coq function to simulate state-mapping information.

>>>>

We construct four families, in one inheritance chain.\YZ{Why is it useful to define these concrete and abstract interpreters as an inheritance chain?}\EDJreply{I don't think these examples are here to show the example themselves are useful. They are here to show family inheritance is useful, and can extend stuff to all sorts of things. I also add some details below on how each family can be extended and what each family means.}\YZreply{Why is it desired to define the abstract interpreter as an extension of the concrete interpreter family? What is lost by putting the two interpreters in the same family?}\EDJreply{Nothing is lost. This is just simulating people starting with bare (big-step) operational semantic. Because they may not working on abstract interpretation from the first place. Those people may extend "Lang" with other stuff like another type-safety proof or something.}

The first family "Lang" define the big step operator (using fuel) of a
while language, with expression. But it postulates the computational
information of "State" (environment mapping) used by Lang. It takes about 200+ LOCs. 
% We
% can
\YZ{In general, in a result section like this, you want to show what
you *have done* rather than what you *can do*.}\EDJreply{Ok. deleted. I initially want to emphasize ``I **can** use arbitrary implementation for this environment mapping interface'' but I don't know how to say that without using ``can''.}
% swap the implementation of "State" to have different memory/state
% management by extending family "Lang".
\YZ{What is 'different
memory/state management'?}\EDJreply{Actually I should say environment mapping/dictionary. I instantiate it with function(closure) as environment mapping in "LangRun". It is possible to use other mapping like Coq's primitive dictionary.}

@@

The fourth family "LangRun" instantiate some of the postulates of the
LangMore and recover computational information of Lang. The concrete
interpreter is doing as expected; the abstract interpreter is expected
to act as a type-analyzer. It takes about 200+ LOCs. This is one example
of instantiate the detail computation. Thanks to the posulation we have done in "Lang", now we instantiate that postulation with function type "Ident -> option exp" as the "State" (environment mapping) for simplicity.
